A Switching Planner for Combined Task and Observation Planning

### 2011-02-05 subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
6-pages!
Moritz, can you add the new experimetns, and perhaps throw away some of the older ones.

\noindent We note that in our project the dual rewards are sourced
from a motivational component of our robotic architecture. In this
paper, for $\assumptiveDT{i}$ actions we set $\$(x)$ to be a positive
constant, and have $\hat\$(x)= - \$(x)(1 - \prob) / \prob$ where
$\prob$ is the probability that $x$ is true. For
$\actions.\poss(\switchAction)$ actions we have $\hat\$(x)= -
\$(x)\prob/(1-\prob)$
%%
Finally, for the purposes of successive switching, execution of either a dual
action of the form $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session, which then continues from the underlying belief-state. If an
assumption was rejected, we prohibit that sequential session from
making it again.
%%

%%  We make no assumptions here about how they are
%% derived.

The starting belief-state for the abstract process is given in terms
of a {\em relaxed} $(\pp{:init})$ declaration. We first construct a
tree which only includes terms from the {\em relaxed} visitation
characterised by the active {\em assumptive} actions in the current
sequential plan. Figure \ref{fig:abstraction} shows the belief-state
of a more detailed version of our previous example. The diamonds
represent probabilistic terms of the state description while circles
represent conjunctive or atomic terms.

@@

  \subfloat[The initial belief-state with the assumptions made by the continual
    planner in bold.]{
      \label{fig:abstraction-a}
    \node[pnode, assumption] (cat) at (1,1) {} [toplevel]
          child {node [cnode] (boxp1) {}}
        child {node [pnode] (cup) {} 
          child {node [cnode] (cupp1) {}}
          child {node [cnode] (cupp2) {}}
      child {node[cnode] (kitchen) {}
        child {node [pnode] (box2) {} 
          child {node [cnode] (box2p1) {}}
          child {node [cnode] (box2p2) {}}
   \node[below=0 of kitchen] {$\pp{kitchen}$};
   \node[below=0 of cup] {$\pp{(is-in cup)}$};
   \node[right=0 of cupp1] {$\pp{place1}$};
   \node[right=0 of cupp2] {$\pp{place2}$};

@@

  \subfloat[Refinement, by adding relevant facts until the $\bstate_0$ size limit is reached.]{

@@

  \caption{Generating the abstract belief space.}
\label{fig:abstraction}
\end{figure}

In the first step, we remove all facts that are not part of an
assumption (Fig. \ref{fig:abstraction-b}). At this point, the session
would proceed in an abstraction of the environment that does not
contain $\pp{place1}$, the $\pp{cup}$ or a $\pp{kitchen}$. 
%%
In a second step, we iteratively refine the relaxed declaration by
adding terms from the original statement of $(\pp{:init})$ while the
number of abstract states in $\bstate_0$ that occur with non-zero
probability according to that refined declaration remains of a
practicable size. In detail, for each excluded atomic term, we compute
the {\em entropy} of the active assumptions, {\em conditional} on the
corresponding proposition.  Loosely speaking, the lower the {\em
  conditional entropy} of an atom, the more information about the
assumptions the contingent planner expect to derive from it. Thus,
propositions that in the first place were excluded are iteratively
added to the problem posed to the conditional session in increasing
order according to that measure (Fig. \ref{fig:abstraction-c}).

%% In detail, for each excluded atomic term, we compute the {\em
%% entropy} of the corresponding proposition, {\em conditional} on the
%% active assumptions. The {\em conditional entropy} measure
%% is higher the more uncertain that proposition is given truth
%% assignments to propositions that are the subject of active
%% assumptions. Propositions that in the first place were excluded are
%% iteratively added to the problem posed to the conditional session in
%% increasing order according to that measure.

%% In particular, we compute the {\em conditional entropy} of
%% each excluded proposition given the active assumptions. Propositions
%% are candidates for addition in increasing order according to that
%% measure.

%% Of course, it is expensive to measure size exactly,
%% and in practise we estimate this to be $2^{|\propositions^\#|}$, where
%% $\propositions^\#$ is the set of propositions in the abstraction that
%% were not assigned the {\em unknown} value \#. Terms are proposed for
%% addition because they are probabilistic, and because they were omitted
%% in the {\em relaxed} visitation characterised by {\em assumptive}
%% actions in the sequential plan. In each iteration, we add one
%% candidate term with the largest number of parent terms already in the
%% candidate tree.

>>>>

\noindent Usually dual rewards are sourced
from a motivational component of our robotic architecture. In this
paper, for $\assumptiveDT{i}$ actions we set $\$(x)$ to be a positive
constant, and have $\hat\$(x)= - \$(x)(1 - \prob) / \prob$ where
$\prob$ is the probability that $x$ is true. For
$\actions.\poss(\switchAction)$ actions we have $\hat\$(x)= -
\$(x)\prob/(1-\prob)$
%%
Finally, execution of either a dual action $\assumptiveDT{i}$, or the
$\actions.\poss(\switchAction)$, returns control to a sequential
session, which then continues from the underlying belief-state. If an
assumption was rejected, we prohibit that sequential session from
making it again.

The process posed to a DT session is abstract. The abstraction is
defined by first constructing an $(\pp{:init})$ declaration without
any-active assumptions from the trace -- E.g.,
(Fig.\ref{fig:abstraction-b}) gives an example, where diamonds are
probabilistic terms, and circles are atomic and/or conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the active
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure
(Fig.\ref{fig:abstraction-c}).

%% In the first step, we remove all facts that are not part of an
%% assumption (Fig. \ref{fig:abstraction-b}). At this point, the session
%% would proceed in an abstraction of the environment that does not
%% contain $\pp{place1}$, the $\pp{cup}$ or a $\pp{kitchen}$. 
%% %%
%% In a second step, we iteratively refine the relaxed declaration by
%% adding terms from the original statement of $(\pp{:init})$ while the
%% number of abstract states in $\bstate_0$ that occur with non-zero
%% probability according to that refined declaration remains of a
%% practicable size. In detail,

@@

  %% \subfloat[The initial belief-state with the assumptions made by the continual
  %%   planner in bold.]{
  %%     \label{fig:abstraction-a}
  %%     \begin{tikzpicture}[
  %%   level 3/.style={tree}]
  %%   \node[pnode, assumption] (cat) at (1,1) {} [toplevel]
  %%     child[seclevel] {node[cnode, assumption] (office) {}
  %%       child {node [pnode, assumption] (box) {}
  %%         child {node [cnode] (boxp1) {}}
  %%         child {node [cnode, assumption] (boxp2) {}}
  %%       }
  %%       child {node [pnode] (cup) {} 
  %%         child {node [cnode] (cupp1) {}}
  %%         child {node [cnode] (cupp2) {}}
  %%       }
  %%     }
  %%     child {node[cnode] (kitchen) {}
  %%       child {node [pnode] (box2) {} 
  %%         child {node [cnode] (box2p1) {}}
  %%         child {node [cnode] (box2p2) {}}
  %%       }
  %%     };
  %%  \tiny
  %%  \draw[assumption] (cat) -- (office) -- (box) -- (boxp2);
  %%  \node[above=0 of cat] {$\pp{(category room1)}$};
  %%  \node[below=0 of kitchen] {$\pp{kitchen}$};
  %%  \node[below=0 of office] {$\pp{office}$};
  %%  \node[below=0 of box] {$\pp{(is-in box)}$};
  %%  \node[below=0 of box2] {$\pp{(is-in box)}$};
  %%  \node[below=0 of cup] {$\pp{(is-in cup)}$};
  %%  \node[right=0 of boxp1] {$\pp{place1}$};
  %%  \node[right=0 of boxp2] {$\pp{place2}$};
  %%  \node[right=0 of box2p1] {$\pp{place1}$};
  %%  \node[right=0 of box2p2] {$\pp{place2}$};
  %%  \node[right=0 of cupp1] {$\pp{place1}$};
  %%  \node[right=0 of cupp2] {$\pp{place2}$};
  %%   % \node[node] (kitchen) right of (cat) {};
  %% \end{tikzpicture}}

@@

  \subfloat[Refinement, by adding relevant facts.]{

@@

  \caption{Abstract belief-state, and refinement.}
\label{fig:abstraction}
\end{figure}
